Stack Safety is a Security Property

### 2021-04-16 tex/main.tex
CP

Together, integrity and confidentiality protect a caller's data until its callee returns
to it. But it is possible that an intermediate caller is never returned to, but returned
{\em past}, to a deeper caller. Fundamentally, this is a control-flow problem, not a
data-protection problem. From that caller's perspective, it is no different from the
callee diverging. But a lower level caller might have been relying on the intermediate
caller to finish its computation, so it is worth protecting control flow even from
attacks that do not violate data protections. We formalize this as {\em return-to-caller}.

>>>>

Together, integrity and confidentiality protect a caller's data until its callee returns
to it. However, it is possible that an intermediate caller is not returned
{\em to}, but rather returned {\em past}, to some ancestor caller! For
example, function $A$ calls function B, which in turn calls $C$, which
returns directly to $A$ by resetting the stack pointer to $A$'s stack frame
and branching to the address after the call from $A$ to $B$.
Strictly speaking, this is not an information-flow problem: the caller's XXXXXX.
\BCP{Still working on this bit.}
But a lower level caller might have been relying on the intermediate
caller to finish its computation, so it is worth protecting control flow even from
attacks that do not violate data protections. We formalize this as {\em return-to-caller}.
